---
title: "Lab2_2030026003"
author: "CaiHuaiyu(Edward)"
date: "2023-03-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

3 In-class exercise
Please download the Salaries.txt from iSpace and complete the following requirements.

# loading package
library(dplyr)
library(readr)

# Please read Salaries data from the file Salaries.csv
# write your answer here

# Select the female professors whose salaries are between 80000 and 100000
# write your answer here

# Calculate the mean of income of professors grouped by sex
# write your answer here

```{r}
# loading package
library(dplyr)
library(readr)

# Please read Salaries data from the file Salaries.csv
# write your answer here

Salaries = read_csv("salaries.csv")
Salaries

# Select the female professors whose salaries are between 80000 and 100000
# write your answer here
#1.Those are Prof and AssProf
newdata <- filter(Salaries, sex == "Female" & salary > 80000 & salary < 100000)
newdata

#2.Those are all Prof
newdata1 <- filter(Salaries, sex == "Female" & salary > 80000 & salary < 100000 & rank == "Prof")
newdata1

# Calculate the mean of income of professors grouped by sex
#1.Those are all Prof
mean_result <- Salaries %>%
  filter(rank == "Prof") %>%
  group_by(sex) %>%
  summarize(mean_income = mean(salary, na.rm=TRUE))
mean_result

#2.Those are Prof and AssProf
mean_result1 <- Salaries %>%
  group_by(sex) %>%
  summarize(mean_income = mean(salary, na.rm=TRUE))
mean_result1
# write your answer here
```

