---
title: "Assignment1_DV"
author: "Ruoxin WANG"
date: "2023-10-19"
output:
  html_document: default
  pdf_document: default
---

#Q1. Installing packages
Please install the following packages in your laptop using the following code (you need fill in the REPLACE part first):

ggplot2, dplyr, tidyr, mosaicData, carData, VIM, scales, treemapify, gapminder, ggmap, choroplethr, choroplethrMaps, CGPfunctions, ggcorrplot, visreg, gcookbook, forcats, survival, survminer, ggalluvial, ggridges, GGally, superheat, waterfalls, factoextra, networkD3, ggthemes, hrbrthemes, ggpol, ggbeeswarm.

Copy the completed codes in the console of RStudio to install all the packages above. Please use the option (eval = FALSE) for the following r code chunk — to not run the code.

```{r eval=FALSE}
# Installing packages: 
pkgs <- c('ggplot2', 'dplyr', 'tidyr', 'mosaicData', 'carData', 'VIM', 'scales', 'treemapify', 'gapminder', 'ggmap', 'choroplethr', 'choroplethrMaps', 'CGPfunctions', 'ggcorrplot', 'visreg', 'gcookbook', 'forcats', 'survival', 'survminer', 'ggalluvial', 'ggridges', 'GGally', 'superheat', 'waterfalls', 'factoextra', 'networkD3', 'ggthemes', 'hrbrthemes', 'ggpol', 'ggbeeswarm')
install.packages(pkgs)
```


#Q2. List
Construct a list that contains 4 components named Zhuhai, Wuhan, Shanghai, Beijing. Each component is a 3-dimensional vector contains weather, highest temporature, lowest temporature, which are given in the output.

```{r}
# Create a list containing weather information for four cities
Zhuhai <- c("Sunny", 30, 20)
Wuhan <- c("Cloudy", 28, 18)
Shanghai <- c("Rainy", 25, 15)
Beijing <- c("Partly Cloudy", 26, 12)

weather <- list(Zhuhai, Wuhan, Shanghai, Beijing)
print(weather)
```


#Q3. Data Frame
Construct a data frame with 4 rows and 4 columns like the output.

```{r}
# Create a data frame
weather <- data.frame(
  city = c("Zhuhai", "Wuhan", "Shanghai", "Beijing"),
  weather = c("Sunny", "Sunny", "Cloudy", "Rainy"),
  high_Tem = c(20, 21, 16, 19),
  low_Tem = c(14, 19, 12, 15)
)

print(weather)
```


#Q4. Reading a File
Read the data from the file Salaries.txt, which has been uploaded in iSpace, and store it into the variable myData.

```{r}
myData <- read.table("Salaries.txt", header = TRUE, sep = "\t")
print(myData[1:5, ])
```


#Q5. Writing Into a File
Write the weather data defined in question 3 into a file named weather.csv. Then read the weather data from this csv file and store in the variable myData.

Hint: You may need to use sep option for write.table.

```{r}
weather <- data.frame(
  city = c("Zhuhai", "Wuhan", "Shanghai", "Beijing"),
  weather = c("Sunny", "Sunny", "Cloudy", "Rainy"),
  high_Tem = c(20, 21, 16, 19),
  low_Tem = c(14, 19, 12, 15)
)

# Write weather data to a CSV file
write.csv(weather, file = "weather.csv", row.names = FALSE)

# Read weather data from the CSV file and store it in myData
myData <- read.csv("weather.csv")
print(myData)
```


#Q6. Data Processing
a. Selecting variables and observations
Please download the data file fuel_economy.csv from the iSpace first. Use the function select in the package dplyr to deal with the fuel economy data.
Hint: Options warning=FALSE, message=FALSE for not displaying the warning messages.

```{r}
# Loading package 
library(dplyr)

# Read fuel economy data from the file named 'fuel_economy.csv' and 
# assign it to the variable 'fuel_eco'
fuel_eco <- read.csv("fuel_economy.csv", header = TRUE, stringsAsFactors = FALSE)

# Select the variables manufacturer, model, year, and fl 
newdata <- fuel_eco %>% select(manufacturer, model, year, fl)

# Print the variable names
print(colnames(newdata))
```

```{r}
# Select all variables except cty and hwy
newdata <- fuel_eco %>% select(-cty, -hwy)

# Print the variable names
print(colnames(newdata))
```

```{r}
# Select the models that are suv classes and contain 4 cylinders (variable: cyl)
newdata <- fuel_eco %>% filter(class == "suv" & cyl == 4)

# Print the selected models
print(newdata)
```

b. Grouping and summarizing data

```{r}
# Calculate the mean displacement (variable: displ) and mean highway miles per gallon (variable: hwy)
newdata <- fuel_eco %>% 
  summarize(mean_displ = mean(displ), mean_hwy = mean(hwy))
newdata
```

```{r}
# Calculate the mean of displ and hwy for 8 cylinders models by manufacturer
newdata <- fuel_eco %>% 
  filter(cyl == 8) %>% 
  group_by(manufacturer) %>% 
  summarize(mean_displ = mean(displ), mean_hwy = mean(hwy))
newdata
```

