---
title: "Lab 1-2 exercise - R basic commands"
author: "Data Visualization (DS4073)"
date: ""
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Q1. The data file “country.txt” in Ispace contains numerous population indicators for a sample of 115 countries.
Read the data file into R and answer the following questions.  
a) How many variables are included in the dataset?  

b) Print the first 11 rows of data.

c) Get the max gdp from data frame.

d) Get the country detail with max gdp.

e) Write the first 20 rows of data to a txt file named "country20.txt".

f) Write the first 20 rows of data to a csv file named "country20.csv".

g) Read 'country20.csv' and check the results.

h) What is the mean of GDP for the developing countries which have death rate higher than 10?

```{r}
data = read.table("country.txt",header=T)
# a)
str(data)
# b) print the first 11 rows of data
head(data, 11)
# c) Get the max gdp from data frame.
maxGDP <- max(data$gdp)
print(maxGDP)
# d) Get the country detail with max gdp
data[which(data$gdp == maxGDP), ]
# e) write the first 20 rows of data to a txt file "country20.txt".
write.table(data[1:20,], file = "country20.txt")
# f) write the first 20 rows of data to a csv file "country20.csv".
write.csv(data[1:20,], file = "country20.csv")
# g) read country20.csv and check the results
myData = read.csv("country20.csv")
print(myData)
# h) What is the mean of GDP for the developing countries which have death rate higher than 10?
attach(data)
mean(gdp[develop==1& deathrate>10])
```

Q2. Fibonacci sequence is defined by F(1)=F(2)=1 and F(n)=F(n–1)+F(n–2). Write an R function called `Fibonacci` which displays the first n Fibonacci numbers and computes their average. For example, if the input n is 20, the output of Fibonacci (20) shall look like:  
The first 20 Fibonacci numbers are:  
1 1 2 3 5 8 13 21 34 55 89 144 233 377 610 987 1597 2584 4181 6765  
The average is 885.5  

```{r}
Fibonacci<-function(n){
  F=c(1,1)
  if (n>=3)
    {for (i in 3:n)
     F[i]=F[i-1]+F[i-2]
     }
  af=mean(F[1:n])
 cat(paste('The first',n,'Fibonacci numbers are:'),'\n',F[1:n],'\n',paste('the average is',af))
}

Fibonacci(20)
```





