---
title: "Nutrition facts of American Fast Food"
author: "Group6"
date: "2023-12-05"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: fill
    social: [ "wechat", "menu"]
    source_code: embed
---

</style>
<style type="text/css">
  body{background:#E1F2FC;}
</style>

```{r}
library(hchinamap)
library(magrittr)
library(ggplot2)
library(plotly)
library(reshape2)
library(dplyr)
library(openintro)
library(highcharter)
library(ggvis)
library(tidyr)
library(readxl)
library(flexdashboard)
library(knitr)
library(DT)
library(rpivotTable)
library(viridis)
library(GGally)
library(rlang)
library(ggcorrplot)
library(ggrepel)
```


```{r, include=FALSE}
# Read CSV file
#df_fat <- read.csv("fat.csv") 
data2 <- read_excel('FastFoodStores.xlsx')

df <- read.csv('FastFoodNutritionMenuV2.csv',encoding="uft_8", sep = ",", check.names=FALSE)
# Replace newline characters in column names with spaces
colnames(df) <- c("Company", "Item", "Calories", "CaloriesFromFat", "TotalFat", "SaturatedFat", "TramsFat", "Cholesterol", "Sodium", "Carbs", "Fiber", "Sugars", "Protein", "WeightWatchersPnts")

# Print missing values before and after dropping a specific column
print(colSums(is.na(df)))
df <- df[,-14]
df <- df[,-4]
print(colSums(is.na(df)))

# Create a collection for special values
special_values_collection <- list()

# Loop through each column starting from the third column (index 2)
for (column in names(df)[3:length(names(df))]) {
  # Initialize the value of the collection to a list
  special_values_collection[[column]] <- c()

  # Iterate through unique values in the column
  for (value in unique(df[[column]])) {
    # Try converting the value to a numeric type
    is_numeric <- suppressWarnings(!is.na(as.numeric(value)))
    
    # If not numeric, add to the special values collection
    if (!is_numeric) {
      special_values_collection[[column]] <- c(special_values_collection[[column]], value)
    }
  }
}

# Loop through columns and update them
for (column in names(df)[3:length(names(df))]) {
  cat("Column: ", column, "\n")
  special_chars <- special_values_collection[[column]]
  values <- as.numeric(df[!(df[[column]] %in% special_chars), column])
  mean_value <- round(mean(values, na.rm = TRUE), 3)
  
  # Fill missing values with the mean
  df[[column]][is.na(df[[column]])] <- mean_value
  
  # Replace special characters with mean or specific value
  for (special_char in special_chars) {
    if (special_char == "<1") {
      df[[column]] <- ifelse(df[[column]] == special_char, 0, df[[column]])
    } else {
      df[[column]] <- ifelse(df[[column]] == special_char, mean_value, df[[column]])
    }
  }
  
  # Convert the column to numeric type
  df[[column]] <- as.numeric(df[[column]])
}

```

```{r, include=FALSE}
McDonald<-subset(df, df$Company== "McDonald’s")
KFC<-subset(df, df$Company== "KFC")
BurgerKing<-subset(df, df$Company== "Burger King")
PizzaHut<-subset(df, df$Company== "Pizza Hut")
TacoBell<-subset(df, df$Company== "Taco Bell")
Wendy<-subset(df, df$Company== "Wendy’s")
```

```{r}
store_counts <- data2 %>%
  group_by(name, province) %>%
  summarise(total_count = n()) %>%
  pivot_wider(names_from = name, values_from = total_count, values_fill = 0) %>%
  mutate(total = rowSums(across(-province)))

br <- store_counts %>%
  select(-province) %>%
  pivot_longer(cols = -total, names_to = "brand", values_to = "counts") %>%
  group_by(brand) %>%
  summarize(total_stores = sum(counts))

#merged <- left_join(store_counts, df_fat, by = "province")
#merged
```


# Overview {data-icon="ion-clipboard"}

## Column {data-hight=200}

### 
```{r}
valueBox(paste("Distribution of Fast-food Restaurant"),
         color = "warning",icon = "ion-android-restaurant")
```

### 
```{r}
custom_colors <- c("#A9DB7F", "#FFCA2C", "#FAD4CF", "#E1F2FC", "#EA9E76", "#FFF3E0")

# 创建直方图
bar_plot <- ggplot(br, aes(x = brand, y = total_stores, fill = brand)) +
  geom_bar(stat = "identity") +
  labs(title = "", x = "Brand", y = "Stores Amount") +
  theme_minimal() +
  scale_fill_manual(values = custom_colors)

# 转换为交互式图表
interactive_bar_plot <- ggplotly(bar_plot)
interactive_bar_plot
```

### 
```{r}
# 创建饼图
pie_chart <- plot_ly(
  labels = br$brand,
  values = br$total_stores,
  type = "pie",
  textinfo = "label+percent",
  insidetextfont = list(color = "black"),
  marker = list(colors =  custom_colors)
) 

# 设置布局
layout <- list(title = "Company Distribution")

# 合并图表和布局
pie_chart <- pie_chart %>% layout(layout)

# 打印饼图
pie_chart
```
## Column 


### 
```{r}
valueBox(paste("Distribution of Nutritional Ingredient"),
         color = "warning",icon = "ion-beer")
```

### 
```{r}
total_summary <- df %>%
  summarize(
    TotalCalories = sum(Calories),
    TotalTotalFat = sum(TotalFat),
    TotalSaturatedFat = sum(SaturatedFat),
    TotalTramsFat = sum(TramsFat),
    TotalCholesterol = sum(Cholesterol),
    TotalSodium = sum(Sodium),
    TotalCarbs = sum(Carbs),
    TotalFiber = sum(Fiber),
    TotalSugars = sum(Sugars),
    TotalProtein = sum(Protein)
  )
total_summary <- pivot_longer(total_summary, cols = everything(), names_to = "Nutrient", values_to = "Value")
total_summary  <- total_summary  %>%
  arrange(desc(Value))
blue_palette <- colorRampPalette(c("#FFF3E0", "#8F2A2A"))
# 生成颜色
co <- blue_palette(length(total_summary$Value))
PIE <- plot_ly(total_summary, labels = ~Nutrient, values = ~Value) %>%
  add_pie(marker = list(colors = co, line = list(color = 'white', width = 0.1)),
          type = 'pie', hole = 0.2,
          textinfo = 'label+percent',
          hoverinfo = 'label+value+percent',
          pull = c(0.05)) %>%
  layout(xaxis = list(zeroline = F, showline = F, showticklabels = F, showgrid = F),
         yaxis = list(zeroline = F, showline = F, showticklabels = F, showgrid = F),height = 560,
  margin = list(l = 90, r = 20, b = 170, t = 10) )
PIE
```

# Nutrient Content of Different Fast-food Restaurants {data-navmenu="Dataset"}

### Nutrient Content of Various Types of Fast Food Restaurants

```{r}
DT::datatable(df,
              rownames = FALSE,
              options = list(pageLength = 5, 
                             scrollY = FALSE),
              class = "display")
```

# Amount of Different Fast-food Restaurants in US {data-navmenu="Dataset"}




###  Amount of Different Fast-food Restaurants in US
```{r}
# 计算每家店在每个省的总数

DT::datatable(store_counts,
              rownames = FALSE,
              options = list(pageLength = 25, 
                             scrollY = FALSE),
              class = "display")
```





# Ingredient Percentage {data-navmenu="Nutritional Ingredient"}

Row
----------------------------------------

```{r, include=FALSE}
MCaverageValues <- colMeans(McDonald[3:12])
MCPieChart <- data.frame(
  Index = names(MCaverageValues),
  AverageValue = as.vector(MCaverageValues)
)

KFCaverageValues <- colMeans(KFC[3:12])
KFCPieChart <- data.frame(
  Index = names(KFCaverageValues),
  AverageValue = as.vector(KFCaverageValues)
)

BKaverageValues <- colMeans(BurgerKing[3:12])
BKPieChart <- data.frame(
  Index = names(BKaverageValues),
  AverageValue = as.vector(BKaverageValues)
)

PHaverageValues <- colMeans(PizzaHut[3:12])
PHPieChart <- data.frame(
  Index = names(PHaverageValues),
  AverageValue = as.vector(PHaverageValues)
)

TBaverageValues <- colMeans(TacoBell[3:12])
TBPieChart <- data.frame(
  Index = names(TBaverageValues),
  AverageValue = as.vector(TBaverageValues)
)

WDaverageValues <- colMeans(Wendy[3:12])
WDPieChart <- data.frame(
  Index = names(WDaverageValues),
  AverageValue = as.vector(WDaverageValues)
)
blue_palette <- colorRampPalette(c("#FFF3E0", "#8F2A2A"))
top_n_items <- 7

```




```{r}
#MC
MCPieChart <- MCPieChart %>%
  arrange(desc(AverageValue)) %>%
  mutate(Index = ifelse(row_number() > top_n_items, "Other", as.character(Index)))

color_values <- ifelse(MCPieChart$Index %in% c("Other", unique(MCPieChart$Index)[1:top_n_items]), blue_palette(length(unique(MCPieChart$Index))), "gray")

MCPIE <- plot_ly(MCPieChart, labels = ~Index, values = ~AverageValue) %>%
  add_pie(marker = list(colors = color_values, line = list(color = 'white', width = 0.1)),
          type = 'pie', hole = 0.2,
          textinfo = 'label+percent',
          hoverinfo = 'label+value+percent',
          pull = c(0.05)) %>%
  layout(xaxis = list(zeroline = F, showline = F, showticklabels = F, showgrid = F),
         yaxis = list(zeroline = F, showline = F, showticklabels = F, showgrid = F),height = 300,
  margin = list(l = 90, r = 20, b = 120, t = 10) )
#KFC
KFCPieChart <- KFCPieChart %>%
  arrange(desc(AverageValue)) %>%
  mutate(Index = ifelse(row_number() > top_n_items, "Other", as.character(Index)))

color_values <- ifelse(KFCPieChart$Index %in% c("Other", unique(KFCPieChart$Index)[1:top_n_items]), blue_palette(length(unique(KFCPieChart$Index))), "gray")

KFCPIE <- plot_ly(KFCPieChart, labels = ~Index, values = ~AverageValue) %>%
  add_pie(marker = list(colors = color_values, line = list(color = 'white', width = 0.25)),
          type = 'pie', hole = 0.2,
          textinfo = 'label+percent',
          hoverinfo = 'label+value+percent',
          pull = c(0.05)) %>%
  layout(xaxis = list(zeroline = F, showline = F, showticklabels = F, showgrid = F),
         yaxis = list(zeroline = F, showline = F, showticklabels = F, showgrid = F),height = 300,
  margin = list(l = 90, r = 50, b = 140, t = 10))

#PH
PHPieChart <- PHPieChart %>%
  arrange(desc(AverageValue)) %>%
  mutate(Index = ifelse(row_number() > top_n_items, "Other", as.character(Index)))

color_values <- ifelse(PHPieChart$Index %in% c("Other", unique(PHPieChart$Index)[1:top_n_items]), blue_palette(length(unique(PHPieChart$Index))), "gray")

PHPIE <- plot_ly(PHPieChart, labels = ~Index, values = ~AverageValue) %>%
  add_pie(marker = list(colors = color_values, line = list(color = 'white', width = 0.25)),
          type = 'pie', hole = 0.2,
          textinfo = 'label+percent',
          hoverinfo = 'label+value+percent',
          pull = c(0.05)) %>%
  layout(xaxis = list(zeroline = F, showline = F, showticklabels = F, showgrid = F),
         yaxis = list(zeroline = F, showline = F, showticklabels = F, showgrid = F),height = 300,
  margin = list(l = 90, r = 50, b = 120, t = 10))

#BK
BKPieChart <- BKPieChart %>%
  arrange(desc(AverageValue)) %>%
  mutate(Index = ifelse(row_number() > top_n_items, "Other", as.character(Index)))

color_values <- ifelse(BKPieChart$Index %in% c("Other", unique(BKPieChart$Index)[1:top_n_items]), blue_palette(length(unique(BKPieChart$Index))), "gray")

BKPIE <- plot_ly(BKPieChart, labels = ~Index, values = ~AverageValue) %>%
  add_pie(marker = list(colors = color_values, line = list(color = 'white', width = 0.25)),
          type = 'pie', hole = 0.2,
          textinfo = 'label+percent',
          hoverinfo = 'label+value+percent',
          pull = c(0.05)) %>%
  layout(xaxis = list(zeroline = F, showline = F, showticklabels = F, showgrid = F),
         yaxis = list(zeroline = F, showline = F, showticklabels = F, showgrid = F),height = 300,
  margin = list(l = 90, r = 50, b = 150, t = 10))

#WD
WDPieChart <- WDPieChart %>%
  arrange(desc(AverageValue)) %>%
  mutate(Index = ifelse(row_number() > top_n_items, "Other", as.character(Index)))

color_values <- ifelse(WDPieChart$Index %in% c("Other", unique(WDPieChart$Index)[1:top_n_items]), blue_palette(length(unique(WDPieChart$Index))), "gray")

WDPIE <- plot_ly(WDPieChart, labels = ~Index, values = ~AverageValue) %>%
  add_pie(marker = list(colors = color_values, line = list(color = 'white', width = 0.25)),
          type = 'pie', hole = 0.2,
          textinfo = 'label+percent',
          hoverinfo = 'label+value+percent',
          pull = c(0.05)) %>%
  layout(xaxis = list(zeroline = F, showline = F, showticklabels = F, showgrid = F),
         yaxis = list(zeroline = F, showline = F, showticklabels = F, showgrid = F),height = 300,
  margin = list(l = 90, r = 50, b = 150, t = 10))

#TB
TBPieChart <- TBPieChart %>%
  arrange(desc(AverageValue)) %>%
  mutate(Index = ifelse(row_number() > top_n_items, "Other", as.character(Index)))

color_values <- ifelse(TBPieChart$Index %in% c("Other", unique(TBPieChart$Index)[1:top_n_items]), blue_palette(length(unique(TBPieChart$Index))), "gray")

TBPIE <- plot_ly(TBPieChart, labels = ~Index, values = ~AverageValue) %>%
  add_pie(marker = list(colors = color_values, line = list(color = 'white', width = 0.20)),
          type = 'pie', hole = 0.2,
          textinfo = 'label+percent',
          hoverinfo = 'label+value+percent',
          pull = c(0.05)) %>%
  layout(xaxis = list(zeroline = F, showline = F, showticklabels = F, showgrid = F),
         yaxis = list(zeroline = F, showline = F, showticklabels = F, showgrid = F),height = 250,
  margin = list(l = 90, r = 50, b = 120, t = 10))

```

### McDanld's
```{r}
MCPIE
```


### KFC

```{r}
KFCPIE
```
Column
----------------------------------------

### Burger King

```{r}
BKPIE
```

### Pizza Hut

```{r}
PHPIE
```


Column
----------------------------------------

### Taco Bell

```{r}
TBPIE
```

### Wendy's

```{r}
WDPIE
```



# Ingredient Distribution {data-navmenu="Nutritional Ingredient"}


Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Calories

```{r}
d_cal <- ggplot(df, aes(x = Company, y = Calories, fill = Company)) +
  geom_violin() +
  labs(title = "Calories Distribution by Company", x = "Company", y = "Calories") +
  theme_minimal()+
  scale_fill_manual(values = custom_colors)
d_cal
```

### Total Fat
```{r}
d_tf <- ggplot(df, aes(x = Company, y = TotalFat, fill = Company)) +
  geom_violin() +
  labs(title = "Total Fat Distribution by Company", x = "Company", y = "TotalFat") +
  theme_minimal()+
  scale_fill_manual(values = custom_colors)
d_tf
```

### Saturated Fat
```{r}
d_sf <- ggplot(df, aes(x = Company, y = SaturatedFat, fill = Company)) +
  geom_violin() +
  labs(title = "Saturated Fat Distribution by Company", x = "Company", y = "SaturatedFat") +
  theme_minimal()+
  scale_fill_manual(values = custom_colors)
d_sf
```

### TramsFat
```{r}
d_trf <- ggplot(df, aes(x = Company, y = TramsFat, fill = Company)) +
  geom_violin() +
  labs(title = "TramsFat Distribution by Company", x = "Company", y = "TramsFat") +
  theme_minimal()+
  scale_fill_manual(values = custom_colors)
d_trf
```

### Cholesterol
```{r}
d_ch <- ggplot(df, aes(x = Company, y = Cholesterol, fill = Company)) +
  geom_violin() +
  labs(title = "Cholesterol Distribution by Company", x = "Company", y = "Cholesterol") +
  theme_minimal()+
  scale_fill_manual(values = custom_colors)
d_ch
```

### Carbs
```{r}
d_cb <- ggplot(df, aes(x = Company, y = Carbs, fill = Company)) +
  geom_violin() +
  labs(title = "Carbs Distribution by Company", x = "Company", y = "Carbs") +
  theme_minimal()+
  scale_fill_manual(values = custom_colors)
d_cb
```

### Fiber
```{r}
d_fb <- ggplot(df, aes(x = Company, y = Fiber, fill = Company)) +
  geom_violin() +
  labs(title = "Fiber Distribution by Company", x = "Company", y = "Fiber") +
  theme_minimal()+
  scale_fill_manual(values = custom_colors)
d_fb
```

### Sugars
```{r}
d_sg <- ggplot(df, aes(x = Company, y = Sugars, fill = Company)) +
  geom_violin() +
  labs(title = "Sugars Distribution by Company", x = "Company", y = "Sugars") +
  theme_minimal()+
  scale_fill_manual(values = custom_colors)
d_sg
```



# Heat Map {data-navmenu="Correlation and Comparison"}

### Heat Map

```{r}

gradient_df <- df[, -c(1,2)]
correlation_matrix <- cor(gradient_df)
correlation_data <- melt(correlation_matrix)

plot_ly(
  data = correlation_data,
  x = ~Var1,
  y = ~Var2,
  z = ~value,
  type = "heatmap",
  colors = colorRamp(c("darkorange1", "white")),
  reversescale = TRUE
) %>%
add_annotations(
  text = ~sprintf("%.2f", value),
  showarrow = FALSE
) %>%
layout(
  title = "Correlation between Components",
  xaxis = list(title = "Components", tickangle = 45),
  yaxis = list(title = "Components"),
  coloraxis = list(zauto = TRUE, zmin = -1, zmax = 1, zmid = 0) 
)
```

# Density Plots {data-navmenu="Correlation and Comparison"} 

```{r}
 #install.packages("gridExtra")
library(gridExtra)

d1 <- df %>%
  ggplot(aes(x = TotalFat, y = Calories)) +
  stat_density_2d(geom = "polygon", aes(fill = ..level..), h = c(100,1500) ,contour = TRUE) +
  scale_fill_viridis(option="magma")
#d1 <- ggplotly(d1)
#d1 <- d1 %>%
#  layout(width = 300, height = 300)

d2 <- df %>%
  ggplot(aes(x = SaturatedFat, y = Calories)) +
  stat_density_2d(geom = "polygon", aes(fill = ..level..), h = c(100,1500) ,contour = TRUE) +
  scale_fill_viridis(option="magma")
#d2 <- ggplotly(d2)
#d2 <- d2 %>%
#  layout(width = 300, height = 300)

d3 <- df %>%
  ggplot(aes(x = TramsFat, y = Calories)) +
  stat_density_2d(geom = "polygon", aes(fill = ..level..), h = c(100,1500) ,contour = TRUE) +
  scale_fill_viridis(option="magma")
#d3 <- ggplotly(d3)
#d3 <- d3 %>%
  #layout(width = 300, height = 300)

d4 <- df %>%
  ggplot(aes(x = Cholesterol, y = Calories)) +
  stat_density_2d(geom = "polygon", aes(fill = ..level..), h = c(100,1500) ,contour = TRUE) +
  scale_fill_viridis(option="magma")
#d4 <- ggplotly(d4)
#d4 <- d4 %>%
#  layout(width = 300, height = 300)

d5 <- df %>%
  ggplot(aes(x = Sodium, y = Calories)) +
  stat_density_2d(geom = "polygon", aes(fill = ..level..), h = c(100,1500) ,contour = TRUE) +
  scale_fill_viridis(option="magma")
#d5<- ggplotly(d5)
#d5 <- d5 %>%
#  layout(width = 300, height = 300)

d6 <- df %>%
  ggplot(aes(x = Carbs, y = Calories)) +
  stat_density_2d(geom = "polygon", aes(fill = ..level..), h = c(100,1500) ,contour = TRUE) +
  scale_fill_viridis(option="magma")
#d6 <- ggplotly(d6)
#d6 <- d6 %>%
  #layout(width = 300, height = 300)


d7 <- df %>%
  ggplot(aes(x = Fiber, y = Calories)) +
  stat_density_2d(geom = "polygon", aes(fill = ..level..), h = c(100,1500) ,contour = TRUE) +
  scale_fill_viridis(option="magma")
#d7 <- ggplotly(d7)
#d7 <- d7 %>%
  #layout(width = 300, height = 300)

d8 <- df %>%
  ggplot(aes(x = Sugars, y = Calories)) +
  stat_density_2d(geom = "polygon", aes(fill = ..level..), h = c(100,1500) ,contour = TRUE) +
  scale_fill_viridis(option="magma")
#d8 <- ggplotly(d8)
#d8 <- d8 %>%
#  layout(width = 300, height = 300)

d9 <- df %>%
  ggplot(aes(x = Protein, y = Calories)) +
  stat_density_2d(geom = "polygon", aes(fill = ..level..), h = c(100,1500) ,contour = TRUE) +
  scale_fill_viridis(option="magma")
#d9 <- ggplotly(d9)
#d9 <- d9 %>%
#  layout(width = 300, height = 300)

# 呈现这些图表
#grid.arrange(d1, d2, d3, d4, d5, d6, d7, d8, d9, nrow = 3, ncol = 3, widths = c(600, 600, 600), heights = c(600, 600, 600))
```
## Column 

### 
```{r}
d1
```

###
```{r}
d2
```

###
```{r}
d3
```

## Column 

### 
```{r}
d4
```

###
```{r}
d5
```

###
```{r}
d6
```

## Column 

### 
```{r}
d7
```

###
```{r}
d8
```

###
```{r}
d9
```




```{r}
MC3D <- plot_ly(McDonald, x = ~Sugars, y = ~Carbs, z = ~Calories, 
                marker = list(color = ~Calories , colorscale = c('#FAD4CF', '#8F2A2A'), showscale = TRUE)) %>%
  add_markers(hoverinfo = "text", text = ~Item) %>%
  layout(scene = list(xaxis = list(title = 'Sugar'),
                      yaxis = list(title = 'Carbohydrates'),
                      zaxis = list(title = 'Calorie')))



KFC3D <- plot_ly(KFC, x = ~Sugars, y = ~Carbs, z = ~Calories, 
                marker = list(color = ~Calories , colorscale = c('#FAD4CF', '#8F2A2A'), showscale = TRUE)) %>%
  add_markers(hoverinfo = "text", text = ~Item) %>%
  layout(scene = list(xaxis = list(title = 'Sugar'),
                      yaxis = list(title = 'Carbohydrates'),
                      zaxis = list(title = 'Calorie')))

BK3D <- plot_ly(BurgerKing, x = ~Sugars, y = ~Carbs, z = ~Calories, 
                marker = list(color = ~Calories , colorscale = c('#FAD4CF', '#8F2A2A'), showscale = TRUE)) %>%
  add_markers(hoverinfo = "text", text = ~Item) %>%
  layout(scene = list(xaxis = list(title = 'Sugar'),
                      yaxis = list(title = 'Carbohydrates'),
                      zaxis = list(title = 'Calorie')))

PH3D <- plot_ly(PizzaHut, x = ~Sugars, y = ~Carbs, z = ~Calories, 
                marker = list(color = ~Calories , colorscale = c('#FAD4CF', '#8F2A2A'), showscale = TRUE)) %>%
  add_markers(hoverinfo = "text", text = ~Item) %>%
  layout(scene = list(xaxis = list(title = 'Sugar'),
                      yaxis = list(title = 'Carbohydrates'),
                      zaxis = list(title = 'Calorie')))

TB3D <- plot_ly(TacoBell, x = ~Sugars, y = ~Carbs, z = ~Calories, 
                marker = list(color = ~Calories , colorscale = c('#FAD4CF', '#8F2A2A'), showscale = TRUE)) %>%
  add_markers(hoverinfo = "text", text = ~Item) %>%
  layout(scene = list(xaxis = list(title = 'Sugar'),
                      yaxis = list(title = 'Carbohydrates'),
                      zaxis = list(title = 'Calorie')))

WD3D <- plot_ly(Wendy, x = ~Sugars, y = ~Carbs, z = ~Calories, 
                marker = list(color = ~Calories , colorscale = c('#FAD4CF', '#8F2A2A'), showscale = TRUE)) %>%
  add_markers(hoverinfo = "text", text = ~Item) %>%
  layout(scene = list(xaxis = list(title = 'Sugar'),
                      yaxis = list(title = 'Carbohydrates'),
                      zaxis = list(title = 'Calorie')))
```

# 3D-Scatter Plot {data-navmenu="Correlation and Comparison"}

Column
----------------------------------------

### McDonald's
```{r}
MC3D
```
### KFC
```{r}
KFC3D
```
Column
----------------------------------------

### Burger King
```{r}
BK3D
```


### Pizza Hut
```{r}
PH3D
```

Column
----------------------------------------

### Taco Bell
```{r}
TB3D
```
### Wendy's
```{r}
WD3D
```

# Fast Food Stores in US {ico="ion-android-globe"}

Column {.tabset .tabset-fade} 
-------------------------------------

### Total Amount of Stores
```{r}
store_counts <- data2 %>%
  group_by(province) %>%
  summarise(total_count = n()) %>%
  arrange(desc(total_count))

base_plot <- ggplot(store_counts, aes(x = reorder(province, -total_count), y = total_count)) +
  geom_bar(stat = "identity", fill = "#EA9E76") +
  labs(title = "Store Counts by Province",
       x = "Province",
       y = "Count") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 8)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  ylim(0, 350)
interactive_plot <- ggplotly(base_plot)
interactive_plot <- interactive_plot %>% layout(height = 400,
  margin = list(l = 50, r = 50, b = 50, t = 50))

interactive_plot
```

### McDonald's
```{r}
store_counts <- data2 %>%
  filter(name == "McDonald's") %>%
  group_by(province) %>%
  summarise(total_count = n()) %>%
  arrange(desc(total_count))

base_plot <- ggplot(store_counts, aes(x = reorder(province, -total_count), y = total_count)) +
  geom_bar(stat = "identity", fill = "#EA9E76") +
  labs(title = "KFC Counts by Province",
       x = "Province",
       y = "Count") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 8)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  ylim(0, 200)
interactive_plot <- ggplotly(base_plot)
interactive_plot <- interactive_plot %>% layout(height = 400,
  margin = list(l = 50, r = 50, b = 60, t = 50))

interactive_plot
```
### KFC
```{r}
store_counts <- data2 %>%
  filter(name == "KFC") %>%
  group_by(province) %>%
  summarise(total_count = n()) %>%
  arrange(desc(total_count))

base_plot <- ggplot(store_counts, aes(x = reorder(province, -total_count), y = total_count)) +
  geom_bar(stat = "identity", fill = "#EA9E76") +
  labs(title = "KFC Counts by Province",
       x = "Province",
       y = "Count") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 8)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  ylim(0, 200)
interactive_plot <- ggplotly(base_plot)
interactive_plot <- interactive_plot %>% layout(height = 400,
  margin = list(l = 50, r = 50, b = 60, t = 50))

interactive_plot
```
### Pizza Hut
```{r}
store_counts <- data2 %>%
  filter(name == "Pizza Hut") %>%
  group_by(province) %>%
  summarise(total_count = n()) %>%
  arrange(desc(total_count))

base_plot <- ggplot(store_counts, aes(x = reorder(province, -total_count), y = total_count)) +
  geom_bar(stat = "identity", fill = "#EA9E76") +
  labs(title = "Pizza Hut Counts by Province",
       x = "Province",
       y = "Count") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 8)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  ylim(0, 200)
interactive_plot <- ggplotly(base_plot)
interactive_plot <- interactive_plot %>% layout(height = 400,
  margin = list(l = 50, r = 50, b = 60, t = 50))

interactive_plot
```
### Wendy's
```{r}
store_counts <- data2 %>%
  filter(name == "Wendy's") %>%
  group_by(province) %>%
  summarise(total_count = n()) %>%
  arrange(desc(total_count))

base_plot <- ggplot(store_counts, aes(x = reorder(province, -total_count), y = total_count)) +
  geom_bar(stat = "identity", fill = "#EA9E76") +
  labs(title = "Wendy's Counts by Province",
       x = "Province",
       y = "Count") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 8)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  ylim(0, 200)
interactive_plot <- ggplotly(base_plot)
interactive_plot <- interactive_plot %>% layout(height = 400,
  margin = list(l = 50, r = 50, b = 60, t = 60))

interactive_plot
```
### Taco Bell
```{r}
store_counts <- data2 %>%
  filter(name == "Taco Bell") %>%
  group_by(province) %>%
  summarise(total_count = n()) %>%
  arrange(desc(total_count))

base_plot <- ggplot(store_counts, aes(x = reorder(province, -total_count), y = total_count)) +
  geom_bar(stat = "identity", fill = "#EA9E76") +
  labs(title = "Taco Bell Counts by Province",
       x = "Province",
       y = "Count") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 8)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  ylim(0, 200)
interactive_plot <- ggplotly(base_plot)
interactive_plot <- interactive_plot %>% layout(height = 400,
  margin = list(l = 50, r = 50, b = 50, t = 50))

interactive_plot
```


### Burger King
```{r}
store_counts <- data2 %>%
  filter(name == "Burger King") %>%
  group_by(province) %>%
  summarise(total_count = n()) %>%
  arrange(desc(total_count))

base_plot <- ggplot(store_counts, aes(x = reorder(province, -total_count), y = total_count)) +
  geom_bar(stat = "identity", fill = "#EA9E76") +
  labs(title = "Burger King Counts by Province",
       x = "Province",
       y = "Count") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 8)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  ylim(0, 200)
interactive_plot <- ggplotly(base_plot)
interactive_plot <- interactive_plot %>% layout(height = 400,
  margin = list(l = 50, r = 50, b = 50, t = 50))

interactive_plot
```

Column {.tabset .tabset-fade}
-------------------------------------
### Total Count
```{r}
store_counts <- data2 %>%
  group_by(name, province) %>%
  summarise(total_count = n()) %>%
  pivot_wider(names_from = name, values_from = total_count, values_fill = 0) %>%
  mutate(total = rowSums(across(-province)))
store_counts <- store_counts %>%
  mutate(count = as.integer(total))
store_counts$hover <- with(store_counts, paste(province, '<br>', "Count:", total, "<br>"))
l <- list(color = rgb(1, 1, 1), width = 2)
g <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = TRUE,
  lakecolor = rgb(1, 1, 1)
)
fig <- plot_geo(store_counts, locationmode = 'USA-states')
color <- colorRampPalette(c("white", "sienna2"))(20)
fig <- fig %>% add_trace(
  z = ~count, text = ~hover, locations = ~province,
  color = ~count, colors = color
)
fig <- fig %>% colorbar(title = "Total Count")
fig <- fig %>% layout(
  title = 'Total Count by State<br>',
  geo = g
)
fig

```

### McDonald's
```{r}
#McDonald's
mc <- data2 %>%
  filter(name == "McDonald's") %>%
  group_by(province) %>%
  summarise(count = n())
mc$hover <- with(mc, paste(province, '<br>', "McDonald's Count:", count, "<br>"))
l <- list(color = rgb(1, 1, 1), width = 2)
g <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = TRUE,
  lakecolor = rgb(1, 1, 1)
)
color <- colorRampPalette(c("white", "sienna2"))(20)
fig <- plot_geo(mc, locationmode = 'USA-states')
fig <- fig %>% add_trace(
  z = ~count, text = ~hover, locations = ~province,
  color = ~count, colors = color
)
fig <- fig %>% colorbar(title = "McDonald's Count")
fig <- fig %>% layout(
  title = 'McDonald\'s Count by State<br>',
  geo = g
)
fig
```

### KFC
```{r}
#KFC
kfc <- data2 %>%
  filter(name == "KFC") %>%
  group_by(province) %>%
  summarise(count = n())
#print(kfc)
kfc$hover <- with(kfc, paste(province, '<br>', "KFC Count:", count, "<br>"))
l <- list(color = rgb(1, 1, 1), width = 2)
g <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = TRUE,
  lakecolor = rgb(1, 1, 1)
)
color <- colorRampPalette(c("white", "sienna2"))(20)
fig <- plot_geo(kfc, locationmode = 'USA-states')
fig <- fig %>% add_trace(
  z = ~count, text = ~hover, locations = ~province,
  color = ~count, colors = color
)
fig <- fig %>% colorbar(title = "KFC Count")
fig <- fig %>% layout(
  title = 'KFC Count by State<br>',
  geo = g
)
fig
```
### Pizza Hut
```{r}
#Pizza Hut
ph <- data2 %>%
  filter(name == "Pizza Hut") %>%
  group_by(province) %>%
  summarise(count = n())
#print(kfc)
ph$hover <- with(ph, paste(province, '<br>', "Pizza Hut Count:", count, "<br>"))
l <- list(color = rgb(1, 1, 1), width = 2)
g <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = TRUE,
  lakecolor = rgb(1, 1, 1)
)
color <- colorRampPalette(c("white", "sienna2"))(20)
fig <- plot_geo(ph, locationmode = 'USA-states')
fig <- fig %>% add_trace(
  z = ~count, text = ~hover, locations = ~province,
  color = ~count, colors = color
)
fig <- fig %>% colorbar(title = "Pizza Hut Count")
fig <- fig %>% layout(
  title = 'Pizza Hut Count by State<br>',
  geo = g
)
fig
```
### Wendy's
```{r}
#Wendy's
w <- data2 %>%
  filter(name == "Wendy's") %>%
  group_by(province) %>%
  summarise(count = n())
#print(kfc)
w$hover <- with(w, paste(province, '<br>', "Wendy's Count:", count, "<br>"))
l <- list(color = rgb(1, 1, 1), width = 2)
g <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = TRUE,
  lakecolor = rgb(1, 1, 1)
)
fig <- plot_geo(w, locationmode = 'USA-states')
color <- colorRampPalette(c("white", "sienna2"))(20)
fig <- fig %>% add_trace(
  z = ~count, text = ~hover, locations = ~province,
  color = ~count, colors = color
)
fig <- fig %>% colorbar(title = "Wendy's Count")
fig <- fig %>% layout(
  title = 'Wendy\'s Count by State<br>',
  geo = g
)
fig
```
### Taco Bell
```{r}
#Taco Bell
tb<- data2 %>%
  filter(name == "Taco Bell") %>%
  group_by(province) %>%
  summarise(count = n())
#print(kfc)
tb$hover <- with(tb, paste(province, '<br>', "Taco Bell Count:", count, "<br>"))
l <- list(color = rgb(1, 1, 1), width = 2)
g <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = TRUE,
  lakecolor = rgb(1, 1, 1)
)
fig <- plot_geo(tb, locationmode = 'USA-states')
color <- colorRampPalette(c("white", "sienna2"))(20)
fig <- fig %>% add_trace(
  z = ~count, text = ~hover, locations = ~province,
  color = ~count, colors = color
)
fig <- fig %>% colorbar(title = "Taco Bell Count")
fig <- fig %>% layout(
  title = 'Taco Bell Count by State<br>',
  geo = g
)
fig
```

### Fat

```{r}
store_counts <- data2 %>%
  group_by(name, province) %>%
  summarise(total_count = n()) %>%
  pivot_wider(names_from = name, values_from = total_count, values_fill = 0) %>%
  mutate(total = rowSums(across(-province)))
store_counts <- store_counts %>%
  mutate(count = as.integer(total))
store_counts$hover <- with(store_counts, paste(province, '<br>', "Count:", total, "<br>"))
l <- list(color = rgb(1, 1, 1), width = 2)
g <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = TRUE,
  lakecolor = rgb(1, 1, 1)
)
fig <- plot_geo(store_counts, locationmode = 'USA-states')
color <- colorRampPalette(c("white", "sienna2"))(20)
fig <- fig %>% add_trace(
  z = ~count, text = ~hover, locations = ~province,
  color = ~count, colors = color
)
fig <- fig %>% colorbar(title = "Total Count")
fig <- fig %>% layout(
  title = 'Total Count by State<br>',
  geo = g
)
fig

```
```{r}
# Replace newline characters in column names with spaces
names(df) <- gsub('\n', ' ', names(df))

# Print missing values before and after dropping a specific column
print(colSums(is.na(df)))
df <- df[, !(names(df) %in% c('Weight Watchers Pnts'))]
print(colSums(is.na(df)))

# Create a collection for special values
special_values_collection <- list()

# Loop through each column starting from the third column (index 2)
for (column in names(df)[3:length(names(df))]) {
  # Initialize the value of the collection to a list
  special_values_collection[[column]] <- c()

  # Iterate through unique values in the column
  for (value in unique(df[[column]])) {
    # Try converting the value to a numeric type
    is_numeric <- suppressWarnings(!is.na(as.numeric(value)))
    
    # If not numeric, add to the special values collection
    if (!is_numeric) {
      special_values_collection[[column]] <- c(special_values_collection[[column]], value)
    }
  }
}

# Loop through columns and update them
for (column in names(df)[3:length(names(df))]) {
  cat("Column: ", column, "\n")
  special_chars <- special_values_collection[[column]]
  values <- as.numeric(df[!(df[[column]] %in% special_chars), column])
  mean_value <- round(mean(values, na.rm = TRUE), 3)
  
  # Fill missing values with the mean
  df[[column]][is.na(df[[column]])] <- mean_value
  
  # Replace special characters with mean or specific value
  for (special_char in special_chars) {
    if (special_char == "<1") {
      df[[column]] <- ifelse(df[[column]] == special_char, 0, df[[column]])
    } else {
      df[[column]] <- ifelse(df[[column]] == special_char, mean_value, df[[column]])
    }
  }
  
  # Convert the column to numeric type
  df[[column]] <- as.numeric(df[[column]])
}

# Print missing values after updating
#print(colSums(is.na(df)))
```

```{r}
library(ggplot2)
library(ggExtra)
library(plotly)

# 假设你已经有了一个名为fast_food_data的数据框，其中包含Calories, Total.Fat..g., 和Company字段

# 创建ggplot对象
p <- ggplot(df, aes(x = Calories, y = TotalFat, color = Company, 
                                 text = paste("Company=", Company, "\nCalories=", Calories, 
                                              "\nTotal Fat (g)=", TotalFat,"\nItem=",Item))) +
  geom_point()

# 将ggplot对象转换为交互式plotly对象
p_interactive <- ggplotly(p, tooltip = "text")

#p_interactive




```

```{r}
a<-max(df$Calories)
b<-min(df$Calories)
df$Calories_group <- cut(df$Calories, breaks=seq(b, a, by=10), include.lowest=TRUE, right=FALSE)
summary_data <- df %>%
  group_by(Calories_group, Company) %>%
  summarise(counts = n(), .groups = 'drop')
# 创建直方图
histogram_plot <- ggplot(df, aes(x = Calories_group, fill = Company,text = paste("Calories Interval=",Calories_group,"\nCompany=", Company))) +
  geom_bar(position="stack", alpha=0.5) +
  theme_minimal()+theme(legend.position = "none") +theme(axis.text.x = element_blank(),axis.title.x = element_blank(),  # Remove x-axis labels
        axis.ticks.x = element_blank(),  # Remove x-axis ticks
        legend.position = "none" )

# 打印图表
h_interactive <- ggplotly(histogram_plot, tooltip = "text")

```

```{r}
a1<-max(df$TotalFat)
b1<-min(df$TotalFat)
df$TotalFat_group <- cut(df$TotalFat, breaks=seq(b, a, by=10), include.lowest=TRUE, right=FALSE)

# 创建一个包含每个区间数据汇总的数据框
summary_data1 <- df %>%
  group_by(TotalFat_group, Company) %>%
  summarise(counts = n(), .groups = 'drop')
# 创建直方图
histogram_plot1<- ggplot(df, aes(x = TotalFat_group, fill = Company,text = paste("Total Fat Interval=",TotalFat_group,"\nCompany=", Company))) +
  geom_bar(position="stack", alpha=0.5) +
  theme_minimal()+theme(axis.text.y  = element_blank(), axis.title.y = element_blank(), # Remove x-axis labels
        axis.ticks.y = element_blank(),  # Remove x-axis ticks
        legend.position ="none" ) +
  coord_flip()

# 打印图表
h_interactive1 <- ggplotly(histogram_plot1, tooltip = "text")

#h_interactive1

```

# Total Fat vs. Calories {data-navmenu="Correlation and Comparison"}

```{r}
library(plotly)

# Create empty plot as a placeholder for where NULL was used
empty_plot <- plotly_empty()

# Assuming h_interactive, p_interactive, and h_interactive1 are your plotly objects
# Create a subplot layout
combined_plot <- subplot(
  list( p_interactive, h_interactive1,h_interactive, empty_plot),
  nrows = 2, # Define two rows
  widths = c(0.7, 0.3), # Define the relative widths of the columns
  heights = c(0.3, 0.7), # Define the relative heights of the rows
  shareX = FALSE, # Share the x-axis among the subplots
  shareY = FALSE, # Do not share the y-axis among the subplots
  titleX = TRUE, # Display the x-axis title
  titleY = TRUE  # Display the y-axis title
)

combined_plot <- combined_plot %>%
  layout(
    xaxis = list(domain = c(0, 0.7)),
    xaxis2 = list(domain = c(0.7, 1)),
    xaxis3 = list(domain = c(0, 0.7), anchor = 'y3'),
    xaxis4 = list(domain = c(0.7, 1), anchor = 'y4'),
    yaxis = list(domain = c(0, 0.7)),
    yaxis2 = list(domain = c(0, 0.7), anchor = 'x2'),
    yaxis3 = list(domain = c(0.7, 1)),
    yaxis4 = list(domain = c(0.7, 1), anchor = 'x4'),
    barmode = 'stack'  # 调整边距
  )

# Print the combined plot
combined_plot


```

```{r}

# Clean the data: Convert columns to numeric, if they are not already
# Assume 'Cholesterol..mg.' and 'Calories' are the correct column names from your dataset
df$Cholesterol <- as.numeric(df$`Cholesterol`)
df$Calories <- as.numeric(df$Calories)

# Create a scatter plot without x-axis labels
B_plot<-ggplot(df, aes(x =Item, y = Cholesterol, size = Calories, color = Calories,text = paste("company=",Company,"\nCalories=",Calories,"\nItems=",Item,"\nCholesterol=",Cholesterol))) +
  geom_point(alpha = 0.7) +  # Make the points semi-transparent
  scale_size(range = c(1, 5)) +  # Adjust the size range for the points
  scale_color_gradient(low = "yellow", high = "red") +  # Color gradient from blue to red
  theme_minimal() +  # Use a minimal theme
  theme(axis.text.x = element_blank(),  # Remove x-axis labels
        axis.ticks.x = element_blank(),  # Remove x-axis ticks
        legend.position = "right")   # Position the legend on the right
  
B_interactive <- ggplotly(B_plot, tooltip = "text")

B_interactive


```
