---
title: "Lab8_2030026150"
author: "Ruoxin WANG"
date: "2023-11-30"
# output: html_document

output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    source_code: embed
---


```{r setup, include=FALSE}
library(flexdashboard)
library(knitr)
library(DT)
library(rpivotTable)
library(ggplot2)
library(plotly)
library(dplyr)
library(openintro)
library(highcharter)
library(ggvis)
library(ggrepel)
```

```{r}
# import dataset from txt file.
data <- read.table("Baseball2010.txt", header = TRUE)
```

```{r}
mycolors <- c("skyblue", "pink", "lightgreen", "purple")
```

Interactive Data Visualization
=====================================

Row
-------------------------------------

### Baseball2010

```{r}
valueBox(paste("Dataset"),
         color = 'dodgerblue')
```

### Total amount of Baseball's team in US

```{r}
valueBox(length(data$Team),
         icon = "fa-user")
```

### **Salary**

```{r}
gauge(round(mean(data$Salary),
            digits = 2),
      min = 0,
      max = 100,
      gaugeSectors(success = c(0, 50),
                   warning = c(50, 80),
                   danger = c(80, 100),
                   colors = c("green", "yellow", "red")))
```

### Total amount of American League
```{r}
valueBox(sum(data$League == 1),
         icon = 'fa-building')
```

### Total amount of National League

```{r}
valueBox(sum(data$League == 0),
         icon = 'fa-building')
```

<!-- ### Size less than 2 -->

<!-- ```{r} -->
<!-- valueBox(sum(data$Size <2), -->
<!--          icon = 'fa-building') -->
<!-- ``` -->

<!-- ### Size larger than 1 -->

<!-- ```{r} -->
<!-- valueBox(sum(data$Size > 1), -->
<!--          icon = 'fa-building') -->
<!-- ``` -->

Row 
-------------------------------

### Wins By Team

```{r}
plot1 <- data %>%
  plot_ly(x = ~Team,
          y = ~Wins,
          color = ~Team,
          type = 'bar') %>%
  layout(xaxis = list(title = "Teams' Name"),
         yaxis = list(title = 'Frequency of Wins'))
plot1

data$Wins
```

### Top Teams

```{r}
plot2 <- data %>%
         group_by(Team) %>%
         filter(Wins>90) %>%
         plot_ly(labels = ~Team,
                 values = ~Wins) %>%
         add_pie(hole = 0.2) %>%
         layout(xaxis = list(zeroline = F,
                             showline = F,
                             showticklabels = F,
                             showgrid = F),
                yaxis = list(zeroline = F,
                             showline = F,
                             showticklabels=F,
                             showgrid=F))
plot2
```

Row 
------------------------------------
### Team Batting Average Vs Team Errors

```{r}
plot3 <- plot_ly(data,
              x = ~Batting,
              y = ~Errors,
              text = paste("Batting:", data$Batting,
                           "Errors:",
                           data$Errors),
              type = "bar") %>%
         layout(xaxis = list(title="Batting"),
                yaxis = list(title = "Errors"),
                plot_bgcolor = "#f5f5f5",
                paper_bgcolor = "#f5f5f5",
                font = list(family = "Arial",
                            size = 12),
                margin = list(l = 50, r = 50,
                              b = 50, t = 50),
                xaxis = list(showgrid = TRUE,
                             gridcolor = "#d3d3d3"),
                yaxis = list(showgrid = TRUE,
                             gridcolor = "#d3d3d3")
                )
plot3

```


### Scatter Plot of ERA Vs Stolen

```{r}
p4 <- plot_ly(data, x=~Stolen) %>%
         add_markers(y = ~ERA,
                     text = ~paste("ERA: ", ERA),
                     showlegend = F) %>%
         add_lines(y = ~fitted(loess(ERA ~ Stolen)),
                   name = "Loess Smoother",
                   color = I("#FFC125"),
                   showlegend = T,
                   line = list(width=5)) %>%
         layout(xaxis = list(title = "Stolen"),
                yaxis = list(title = "ERA"))
p4
```



Bubble Salary Vs Wins
========================================

### Bubble Salary Vs Wins by different size team

```{r}
ggplot(data=data,aes(x=Salary,y=Wins))+
  geom_point(aes(size=Size,fill=Size),shape=21,colour="black",alpha=0.8)+
  scale_fill_gradient2(low="#377EB8",high="#E41A1C",limits=c(0,max(data$Size)),
                       midpoint=mean(data$Size))+
  scale_size_area(max_size=12)+
  geom_text_repel(aes(label = Size), color = "black", size = 3, fontface = "bold") +
  theme_minimal() +
  labs(x = "Salary", y = "Wins", title = "Salary vs. Wins") +
  theme(plot.title = element_text(size = 20, hjust = 0.5), legend.position = "bottom")
```

Data Table
========================================

```{r}
datatable(data,
          caption = "Baseball Data in 2010",
          rownames = T,
          filter = "top",
          options = list(pageLength = 25))
```

Summary {data-orientation=columns} 
===========================================

Column 
-----------------------------------

### Max Size among team

```{r}
valueBox(max(data$Size),
         icon = "fa-user" )
```
### Average Size among team

```{r}
valueBox(mean(data$Size),
         icon = "fa-area-chart" )
```


### Average Attendance among team
```{r}
valueBox(round(mean(data$Attendance),
               digits = 2),
         icon = "fa-area-chart")
```

### Average HR among team

```{r}
valueBox(round(mean(data$HR), digits = 2),
         icon = "fa-area-chart")
```

Column
---------------------------

Report

* This is a report on `r length(data$Team)` team.

* The max size among team was `r max(data$size)`.

* The average size among team was `r mean(data$Size)`.

* The average attendance among team was `r mean(data$Attendance)`.

* The average HR among team was `r mean(data$HR)`.

This report was generated on `r format(Sys.Date(), format = "%B %d, %Y")`.