---
title: "Lab 1-2 Exercise - R Basic Commands"
author: "Data Visualization (DS4073)"
date: "2023/09/27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---

**Please input your student name and No. below.**    
**Student Name: Ruoxin WANG **  
**Student No.: 2030026150 **  

---


Q1. The data file “country.txt” in Ispace contains numerous population indicators for a sample of 115 countries.
Read the data file into R and answer the following questions.  

a) How many variables are included in the dataset?  
```{r}
data <- read.table("country.txt", head=TRUE)
print(ncol(data))
```

b) Print the first 11 rows of data.
```{r}
head(data, 11)
```

c) Get the max gdp from data frame.
```{r}
max_res <- max(data$gdp)
print(max_res)
```

d) Get the country detail with max gdp.
```{r}
detail_res <- data[which(data$gdp == max_res), ]
print(detail_res)
```

e) Write the first 20 rows of data to a txt file named "country20.txt".
```{r}
write.table(head(data, 20), file = "country20.txt")
```

f) Write the first 20 rows of data to a csv file named "country20.csv".
```{r}
write.csv(head(data, 20), file = "country20.csv", row.names = FALSE)
```

g) Read 'country20.csv' and check the results.
```{r}
csv_data <- read.csv("country20.csv", header = TRUE)
csv_data
```

h) What is the mean of GDP for the developing countries which have death rate higher than 10?
```{r}
dr <- data[which(data$deathrate>10), ]
mean_res <- mean(dr[which(dr['develop']==1), 'gdp'])
print(mean_res)
```


Q2. Fibonacci sequence is defined by F(1)=F(2)=1 and F(n)=F(n–1)+F(n–2). Write an R function called `Fibonacci` which displays the first n Fibonacci numbers and computes their average. For example, if the input n is 20, the output of Fibonacci (20) shall look like:  
The first 20 Fibonacci numbers are:  
1 1 2 3 5 8 13 21 34 55 89 144 233 377 610 987 1597 2584 4181 6765  
The average is 885.5  

```{r}
# write your answer here
Fibonacci <- function(n) {
  f <- c()
  f[1] <- 1
  f[2] <- 1
  if(n == 1 | n == 2) {
    f[n] <- f[n]
    return(f)
  } else {
    for(i in 3:n) {
      f[i] <- f[i-1] + f[i-2]
    }
    return (f)
  }
}
# print out the result.
print(Fibonacci(20))
print(mean(Fibonacci(20)))
```





