---
title: "DV_Lab4"
author: "Ruoxin WANG"
date: "2023-11-07"
output: html_document
---

Please complete the codes such that they can produce the same outputs.
Submit the .rmd and .html files to iSpace.

1. Please plot a bar chart for the variable ‘sign’ from the Marriage dataset.
Hint: Notice the labels of x and y axes.
```{r}
#install.packages("mosaicData")
```

```{r}
# Loading package
library(ggplot2)
library(dplyr)

# Loading data
data(Marriage, package = "mosaicData")

# Write your code here
sign_data <- Marriage %>%
  count(sign) %>%
  arrange(desc(n))

plt1 <- ggplot(sign_data, 
       aes(x = reorder(sign, -n), 
           y = n)) + 
  geom_bar(stat = "identity") +
  labs(x = "Astrological sign", 
       y = "Frequency", 
       title  = "Astrological sign of bride/groom") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  geom_text(aes(label = n), vjust = -0.5)

print(plt1)
```


2. Please flip the x and y axes, and modify the fill and border colors for all the bars. Change the theme to the classic type theme_classic().
** Hint**: The colors lightblue and white may help. Notice the x and y labels.

```{r}
# Bar chart with flipping x and y and 
# change the fill and border colors for all bars
# Write your code here
plt2 <- ggplot(sign_data, 
              aes(x = n,
                  y = reorder(sign, n))) +
  geom_bar(stat = "identity", fill = "lightblue", color = "white") +
  geom_text(aes(label = n), position = position_dodge(width = 0.9), hjust = -1) +
  labs(x = "Frequency",
       y = "Astrological sign",
       title = "Astrological sign of bride/groom") +
  theme_classic()

print(plt2)

```

3. Which astrological sign has the highest proportion? Which astrological sign has the lowest proportion? Please calculate their proportions using R codes.
```{r}
# Write your code here
# use table to calculate count of each astrological.
sign_counts <- table(Marriage$sign)

# calculate the proportion of each astrological.
sign_proportions <- sign_counts / sum(sign_counts)

# find the astrological which have highest and lowest proportion.
max_proportion_sign <- names(sign_proportions[sign_proportions == max(sign_proportions)])
min_proportion_sign <- names(sign_proportions[sign_proportions == min(sign_proportions)])

# display results.
cat("The astrological sigh which has the highest proportion: ", max_proportion_sign, "\n")
cat("The highest proportion:", max(sign_proportions), "\n")
cat("The astrological sigh which has the lowest proportion: ", min_proportion_sign, "\n")
cat("The lowest proportion:", min(sign_proportions), "\n")
```



